Supplement to Automatic Matching of Bullet Lands

### 2016-01-05 imaging-supplement.Rnw
moved table to supplement

@@

aligned <- crossSmooth %>% group_by(id) %>% do(
  data.frame(alignme(.))
)
aligned$land <- (aligned$id %% 6)
aligned$land[aligned$land==0] <- 6
qplot(x=y, y=l30, data=aligned, geom="line", group=bullet) + ylim(c(-7,7)) + facet_grid(facets=barrel~land, labeller="label_both") + theme_bw() +
  xlab("") + ylab("Signature") + 
  theme(plot.margin=unit(c(0,0,0,0), unit="cm"))
@
\caption{\label{fig:aligned}Overview of aligned signatures for all bullet lands for the ten barrels of the Hamby study. }
\end{figure}
\bibliographystyle{imsart-nameyear.bst}
%\biboptions{authoryear}
\bibliography{references}

>>>>

\usepackage{dcolumn}
\newcolumntype{d}[1]{D{.}{.}{#1}}

@@

aligned <- crossSmooth %>% group_by(id) %>% do(
  data.frame(alignme(.))
)
aligned$land <- (aligned$id %% 6)
aligned$land[aligned$land==0] <- 6
qplot(x=y, y=l30, data=aligned, geom="line", group=bullet) + ylim(c(-7,7)) + facet_grid(facets=barrel~land, labeller="label_both") + theme_bw() +
  xlab("") + ylab("Signature") + 
  theme(plot.margin=unit(c(0,0,0,0), unit="cm"))
@
\caption{\label{fig:aligned}Overview of aligned signatures for all bullet lands for the ten barrels of the Hamby study. }
\end{figure}

\newpage
\section{Results from Random Forest}\label{supp:randomforest}

<<setup-rtrees, echo=FALSE, message=FALSE>>=
bstats <- read.csv("data-25-25/bullet-stats.csv", stringsAsFactors = FALSE)

library(randomForest)
set.seed(20151202)
includesVar <- setdiff(names(bstats), c("b1", "b2", "data", "resID", "id.x", "id.y", "pred", "forest", "bullet", "span", "crosscutdist", "flagged", "km"))

rtrees <- randomForest(factor(match)~., data=subset(bstats, !flagged)[,includesVar], ntree=300)
@

\begin{table}[tbhp]
\caption{\label{tab:importance}Table of  features derived from bullet image ordered by importance in predicting matches. Importance is measured in terms of mean decrease in gini index when including the variable in a decision tree. Averages (and standard deviations) for known matches (KM) and known non-matches (KNM) are shown in the last four columns.}
\centering
<<importance, echo=FALSE, results='asis', warning=FALSE>>=
imp <- data.frame(importance(rtrees))
imp$Variable <- row.names(imp)
imp <- imp[order(-imp$MeanDecreaseGini),]
names(imp)[1] <- "Importance"
imp <- imp[,2:1]
imp$meanMatch <- sapply(imp$Variable, function(var) {
  mean(subset(bstats, match)[,var])
})
imp$sdMatch <- sapply(imp$Variable, function(var) {
  sd(subset(bstats, match)[,var])
})
imp$meanNonMatch <- sapply(imp$Variable, function(var) {
  mean(subset(bstats, !match)[,var])
})
imp$sdNonMatch <- sapply(imp$Variable, function(var) {
  sd(subset(bstats, !match)[,var])
})
imp$meanMatch <- round(imp$meanMatch,1)
imp$sdMatch <- sprintf("(%5.2f)", imp$sdMatch)
imp$meanNonMatch <- round(imp$meanNonMatch,1)
imp$sdNonMatch <- sprintf("(%7.2f)", imp$sdNonMatch)
row.names(imp) <- 1:nrow(imp)
imp$Variable[c(2,4)] <- c("#matches", "#non-matches")
names(imp)[-(1:2)] <- c("KM", "(sd)", "KNM", "(sd)")
print(xtable(imp, align="clrrd{3.2}rd{3.2}", digits=c(0,0,1,1,2,1,2)), 
      floating = FALSE)
@
\end{table}

\bibliographystyle{imsart-nameyear.bst}
%\biboptions{authoryear}
\bibliography{references}
